A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex
clarifying point

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields)

@@

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.

>>>>

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

@@

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
